E Coli Project Paper Incredibly Rough Draft

### 2013-09-04 paper/paper.tex
changes to paper and bib Tested everything on node26.

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper is about science.
\end{abstract}
\section{Introduction}
It is vital that during the process of bacterial cell division a
cell avoid minicelling, or splitting into daughter cells with lopsided
volumes.  During this process a long FtsZ polymer chain develops on
the cell wall in the center region of the cell which acts as a guide
for the division. Previous experimental studies have shown
that the MinC protein, known to inhibit the FtZ polymer, exhibits a
pole to pole oscillatory behavoir in conjunction with the MinD and
MinE proteins, while the oscillating MinE tends to be more localized
in the center of the cell \cite{hu1999topological} \cite{fu2001mine}
The MinC protein will then have a higher time averaged
concentration in the cell poles as opposed to the center region of the
cell, prohibiting the FtZ from building in the wrong region.

@@

@@

It is vital for the mechanism by which the cell accurately divides to
be robust and indeed it has been shown to
be\cite{touhami2006temperature}.  Studies have shown that the
oscillations can effectively find poles in abberent cell
shapes\cite{varma2008min}\cite{juarez2010changes}.  However, Mannik et
al. have shown that there are limits to this robustness. Forcing cells
into flattened, irregular cell shapes adversly effects the Min
system's ability to maintain their regular oscillatory
behavior\cite{mannik2012robustness}\cite{mannik2009bacterial}.  We
follow the experimental work of Mannik et and use Huang's mean field
differential equation reaction model to explore the model's ability to
find regular oscillatory behavoir in a series of abberent shapes.

>>>>

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  This paper is about science.
\end{abstract}
\section{Introduction}
It is vital that during the process of bacterial cell division a cell
avoid minicelling, or splitting into daughter cells with lopsided
volumes.  During this process a long FtsZ polymer chain develops on
the cell wall in the center region of the cell that dictates the plane
of division\cite{adams2009bacterial}
\cite{lutkenhaus2007assembly}. Previous experimental studies have
shown that the MinC protein, known to inhibit the FtZ
polymer\cite{shen2010examination}, exhibits a pole to pole oscillatory
behavoir in conjunction with the MinD and MinE proteins, while the
oscillating MinE tends to be more localized in the center of the cell
\cite{hu1999topological} \cite{fu2001mine} \cite{shapiro2009and}
\cite{yu1999ftsz} \cite{raskin1999rapid}The MinC protein will then have a higher time
averaged concentration in the cell poles as opposed to the center
region of the cell, aiding in prohibiting the FtZ from developing in the wrong
region.

@@

\fixme{should read following citation more carefully, worried -
  abstract says that simple models don't explain certain experimental
  findings.} \cite{ivanov2010multiple}

@@

It is vital for the mechanism by which the cell accurately divides to
be robust and indeed it has been shown to
be\cite{touhami2006temperature}.  Studies have shown that the
oscillations can effectively find poles in abberent cell
shapes\cite{varma2008min}\cite{juarez2010changes}.  However, Mannik et
al. have shown that there are limits to this robustness. Forcing cells
into flattened, irregular cell shapes adversly effects the Min
system's ability to maintain their regular oscillatory
behavior\cite{mannik2012robustness} \cite{mannik2010bacteria} \cite{mannik2009bacterial}.  We
follow the experimental work of Mannik et and use Huang's mean field
differential equation reaction model to explore the model's ability to
find regular oscillatory behavoir in a series of abberent shapes.
